\begin{itemize}[itemsep=0.5ex]
    
\item[--] Elected member, {\em Sociological Research Association}, 2019. 

\item[--] (with Michael Strand), American Sociological Association Section on Theory {\em Theory Prize for Outstanding Article} for ``Beyond world images: Belief as embodied action in the world'' (Honorable Mention), 2017.

\item[--] (with Jessica Collett), American Sociological Association Section on Emotions {\em Recent Contribution Award} for ``Embarrassment and social organization: A multiple identities model'' (Honorable Mention), 2015.

\item[--] (with Robert Fishman), American Sociological Association Section on Comparative and Historical Sociology {\em Charles Tilly Best Article Award} for ```How macro-historical change shapes cultural taste: Legacies of democratization in Spain and Portugal,'' 2014.

\item[--] (with Aaron Striegel, Shu Liu, Lei meng, Christian Poelleabauer, and David Hachen) Best Paper Award at The Fifth ACM Hotplanet Workshop, Hong Kong 2013.

\item[--] American Sociological Association Section on Theory {\em Lewis Coser Award for Theoretical Agenda Setting}, 2013.

\item[--] American Sociological Association Section on Culture  {\em Clifford Geertz Prize for Best Article} for ``How cultural tastes shape personal networks,'' 2008.

\item[--] (with Jessica Collett), American Sociological Association Section on Religion  {\em Best Graduate Student Paper Award} for ``Why biology is not (religious) destiny: a second look at gender differences in religiosity,''   2005.

\item[--] (with Jessica Collett), American Sociological Association Section on Emotions  {\em Best Graduate Student Paper Award} for ``Socioeconomic status and the experience of anger,'' 2005.

\item[--] University of Arizona Department of Sociology's  {\em Raymond V. Bowers Graduate Student Paper Competition} for ``Why biology is not (religious) destiny: a second look at gender differences in religiosity,'' 2005.

\item[--] University of Arizona Department of Sociology's  {\em Raymond V. Bowers Graduate Student Paper Competition} for ``The effect of employment status on gender differences in culture consumption,'' 2003.

\item[--] {\em Student Paper Competition}, Graduate Division General Social Survey for ``The effect of employment status on gender differences in culture consumption'' (Honorable Mention), 2003.
\end{itemize}