
\ind Jessica Collett and {\bf Omar Lizardo}. ``Localizing cultural phenomena by specifying social psychological mechanisms: Introduction to the special issue.'' {\em Social Psychology Quarterly} 77: 95-99. \href{https://doi.org/10.1177/0190272514529409}{\nolinkurl{doi:10.1177/0190272514529409}}.

\ind {\bf Omar Lizardo}. ``Foreword.'' Pp. vii-xii in Adam Isaiah Green (Ed.), {\em Sexual Fields: Toward a Sociology of Collective Sexual Life}. The University of Chicago Press.

\ind {\bf Omar Lizardo}. ``Beyond the Comtean schema: The sociology of culture and cognition versus cognitive social science.''  {\em Sociological Forum} 29: 983–989. \href{https://doi.org/10.1111/socf.12130}{\nolinkurl{doi:10.1111/socf.12130}}.

\ind {\bf Omar Lizardo}. ``Theorizing and cognitive science.'' {\em Perspectives: Newsletter of the ASA Theory Section} 36(1).

\ind {\bf Omar Lizardo}.  ``Social psychological processes as mechanisms for the explanation of cultural phenomena.'' \emph{Culture: Newsletter of the Sociology of Culture Section of the American Sociological Association} 26(1): Spring 2013. \href{https://asaculturesection.files.wordpress.com/2018/03/2013a_spring.pdf}{\nolinkurl{https://asaculturesection/2013a_spring.pdf}}

\ind {\bf Omar Lizardo}. ``What young people should know about theory and theorizing today.'' {\em Perspectives: Newsletter of the ASA Theory Section} 34(2).

\ind {\bf Omar Lizardo} and Terence McDonnell. ``Culture warriors: Cultural sociology at Notre Dame University.'' \emph{Culture: Newsletter of the Sociology of Culture Section of the American Sociological Association} 25(3).  \href{https://asaculturesection.files.wordpress.com/2018/03/2012c_fall.pdf}{\nolinkurl{https://asaculturesection/2012c_fall.pdf}}

\ind {\bf Omar Lizardo}.  ``Analytical sociology’s superfluous revolution: Comment on Little.'' {\em Sociologica: International Journal for Sociological Debate} 1/2012. \href{https://www.rivisteweb.it/doi/10.2383/36902}{\nolinkurl{doi: 10.2383/36902}}
 
\ind {\bf Omar Lizardo}. ``The three phases of Bourdieu's American reception:  Comment on Lamont.''  {\em Sociological Forum} 27: 238-244. \href{https://doi.org/10.1111/j.1573-7861.2011.01310.x}{\nolinkurl{doi: 10.1111/j.1573-7861.2011.01310.x}}.
 