
\ind Matteo Serafino, G. Virginio Clemente, James Flamino, Boles\l{}aw K. Szyma\'{n}ski, {\bf Omar Lizardo} and Hern\'{a}n A. Makse. ``Analysis of flows in social media uncovers a new
multi-step model of information spread.'' \href{https://arxiv.org/abs/2409.01225}{\nolinkurl{arXiv:2409.01225}}.

\ind Mateusz Nurek, Joanna Ko\l{}aczek, Rados\l{}aw Michalski, Boles\l{}aw K. Szyma\'{n}ski and {\bf Omar Lizardo}. ``CoDiNG -- Naming game with continuous latent state of agents.'' \href{https://arxiv.org/abs/2406.19204}{\nolinkurl{arXiv:2406.19204}}.

\ind James Flamino, Ross DeVito, {\bf Omar Lizardo} and Boles\l{}aw K. Szyma\'{n}ski. ``Modeling memory imprints induced by interactions in social networks.'' \href{https://arxiv.org/abs/2101.09417}{\nolinkurl{arXiv:2101.09417}}.

\ind James Flamino, Ross DeVito, Boles\l{}aw K. Szyma\'{n}ski and {\bf Omar Lizardo}. ``A machine learning approach to predicting continuous tie strengths.'' \href{https://arxiv.org/abs/2101.09417}{\nolinkurl{arXiv:2101.09417}}.

\ind Mateusz Nurek, Rados\l{}aw Michalski, {\bf Omar Lizardo} and Marian-Andrei Rizoiu. ``Predicting Relationship Labels and Individual Personality Traits from Telecommunication History in Social Networks using Hawkes Processes.'' \href{https://arxiv.org/abs/2009.02032}{\nolinkurl{arXiv:2009.02032}}.

\ind Shikang Liu, David Hachen, {\bf Omar Lizardo}, Christian Poellabauer, Aaron Striegel and Tijana Milenkovic. ``The power of dynamic social networks to predict individuals' mental health.'' \href{https://arxiv.org/abs/1908.02614}{\nolinkurl{arXiv:1908.02614}}.

\ind Shikang Liu, Fatemeh Vahedian, David Hachen, {\bf Omar Lizardo}, Christian Poellabauer, Aaron Striegel and Tijana Milenkovic. ``Heterogeneous network approach to predict individuals' mental health.'' \href{https://arxiv.org/abs/1906.04346}{\nolinkurl{arXiv:1906.04346}}.

\ind Rados\l{}aw Michalski, Boles\l{}aw K. Szyma\'{n}ski, Przemys\l{}aw Kazienko, Christian Lebiere, {\bf Omar Lizardo} and Marcin Kulisiewicz. ``Social networks through the prism of cognition.'' \href{https://arxiv.org/abs/1806.04658}{\nolinkurl{arXiv:1806.04658}}.

\ind Louis Faust, Priscilla Jim\'{e}nez, David Hachen, {\bf Omar Lizardo}, Aaron Striegel, and Nitesh V. Chawla. ``Long-term compliance habits: What early data tells us.'' \href{https://arxiv.org/abs/1804.04256}{\nolinkurl{arXiv:1804.04256}}.

\ind Ashwin Bahulkar, Boles\l{}aw K. Szyma\'{n}ski, Nitesh Chawla, {\bf Omar Lizardo} and Kevin Chan. ``Influence of Personal Preferences on Link Dynamics in Social Networks.'' \href{https://arxiv.org/abs/1709.07401}{\nolinkurl{arXiv:1709.07401}}.

\ind Ashwin Bahulkar, Boles\l{}aw K. Szyma\'{n}ski, {\bf Omar Lizardo}, Yuxiao Dong, Yang Yang and Nitesh V. Chawla. ``Analysis of link formation, persistence and dissolution in NetSense Data.'' \href{https://arxiv.org/abs/1611.00568}{\nolinkurl{arXiv:1611.00568}}.

\ind Yang Yang, {\bf Omar Lizardo}, Dong Wang, Yuxiao Dong, Aaron D. Striegel, David Hachen, and Nitesh V. Chawla. ``Gender differences in communication behaviors, spatial proximity patterns, and mobility habits." 2016. \href{https://arxiv.org/abs/1607.06740}{\nolinkurl{arXiv:1607.06740}}.

\ind Yuxiao Dong, {\bf Omar Lizardo}, Nitesh V. Chawla. ``Do the young live in a `smaller world' than the old? Age-specific degrees of separation in a large-scale Mobile communication network.'' \href{https://arxiv.org/abs/1606.07556}{\nolinkurl{arXiv:1606.07556}}.

\ind  Cheng Wang, Anthony Strathman, {\bf Omar Lizardo}, David Hachen, Zoltan Toroczkai and Nitesh V. Chawla. ``Weighted reciprocity in human communication networks.'' \href{https://arxiv.org/abs/1108.2822}{\nolinkurl{arXiv:1108.2822}}.

\ind Troy Raeder, {\bf Omar Lizardo}, David Hachen and Nitesh V. Chawla. ``Predictors of short-term decay of cell phone contacts in a large scale communication network.'' \href{https://arxiv.org/abs/1102.1753}{\nolinkurl{arXiv:1102.1753}}.
