
\ind ``The future of Sociology as a discipline.'' Presidential Plenary,  Annual Meeting of the Southern Sociological Society, Charlotte, NC, 2025.

\ind ``Publishing in top disciplinary journals in Sociology." Professional Development Workshop, McGill Desautels Faculty of Management, Montreal, 2024.

\ind ``Professional taste: Omnivorousness, empathy, and possibility in the structure of evaluation.'' 
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
    \setlength\itemsep{-0.55em}
        \item[--] {\em Northwestern Sociology Colloquium Speaker Series}, Northwestern University, Evanston, IL, 2025.
        \item[--] {\em Seminar Series of the Institute for Analytical Sociology}, Norrk\"{o}ping, Sweden, 2024 (Remote).
        \item[--] {\em McGill Desautels Faculty of Management Speaker Series}, McGill University, Montreal, 2024.
        \item[--] {\em UCSD's Sociology Colloquium Speaker Series}, University of California, San Diego, CA, 2024. 
\end{itemize}

\ind ``Coasting on duality: What we get when we do two-mode (network) CA.'' 

\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
    \setlength\itemsep{-0.55em}
        \item[--] {\em Wolfwebs Speaker Series}, North Carolina State University, Raleigh, NC, 2024. 
	\item[--] {\em Duality@50 Workshop: Making progress and looking forward}, Hotel and Congress Center Monte Verit\'{a} Ascona, Switzerland, 2024.
\end{itemize}

\ind ``The past, present, and future of culture and cognition work in Sociology.'' {\em Conference on What is the Future of Culture and Cognition?} Rutgers University, New Brunswick, NJ, 2023 (remote). 

\ind ``Omnivorous taste as category-mediated performance."  
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
    \setlength\itemsep{-0.55em}
        \item[--] {Sociology Department Seminar Series}, John Hopkins University, Baltimore, MD, 2023.
	\item[--] {\em FSU Sociology Colloquium Series}, Florida State University, Tallahassee, FL, 2023.
 	\item[--] {\em Yale Computational Social Science Workshop}, Yale University, New Haven, CT, 2022.
\end{itemize}

\ind ``Between Embodiment and Categorization: The `omnivore thesis' revisited." {\em Joint Degree Program in Social Policy, Dilemmas of Inequality Lecture/Workshop Series}, Princeton University, Princeton, NJ, 2022. 

\ind Panelist, Roundtable on ``Cultural Change and Democracy.'' {\em Twenty-Eighth International Conference of Europeanists}, Lisbon, Portugal, 2022. 

\ind Panelist, Author Meets Critics/Book, Power in Modernity: Agency Relations and the Creative Destruction of the King's Two Bodies by Isaac Ariail Reed. {\em Annual Meeting of the Social Science History Association}, Philadelphia, PA, 2021.

\ind ``The structures of taste: The `omnivore thesis' revisited.'' {\em Sociology Department Colloquium Series, University of Texas, Austin}, 2021 (remote). 

\ind ``Discovering microgenre communities in survey data on cultural practices.'' {\em University of Notre Dame Sociology Department Culture Workshop}, 2021 (remote).

\ind ``What's wrong with social psychology?'' {\em Virtual Annual Meeting of the American Sociological Association}, 2021 (remote).

\ind ``Inspired by: Pierre Bourdieu (1980, 1983, 1985).'' {\em Virtual Miniconference on the Social Logic of the Demand and Supply of Authenticity}, 2021 (remote).