
\ind ``The past, present, and future of culture and cognition work in Sociology.'' {\em Conference on What is the Future of Culture and Cognition?} Rutgers University, New Brunswick, NJ, 2023 (remote). 

\ind ``Omnivorous taste as category-mediated performance."  
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em Yale Computational social Science Workshop}, Yale University, New Haven, CT, 2022.
	\item[--] {\em FSU Sociology Colloquium Series}, Florida State University, Tallahassee, FL, 2023.
\end{itemize}

\ind ``Between Embodiment and Categorization: The `omnivore thesis' revisited." {\em Joint Degree Program in Social Policy, Dilemmas of Inequality Lecture/Workshop Series}, Princeton University, Princeton, NJ, 2022. 

\ind Panelist, Roundtable on ``Cultural Change and Democracy.'' {\em Twenty-Eighth International Conference of Europeanists}, Lisbon, Portugal, 2022. 

\ind Panelist, Author Meets Critics/Book, Power in Modernity: Agency Relations and the Creative Destruction of the King's Two Bodies by Isaac Ariail Reed. {\em Annual Meeting of the Social Science History Association}, Philadelphia, PA, 2021.

\ind ``The structures of taste: The `omnivore thesis' revisited.'' {\em Sociology Department Colloquium Series, University of Texas, Austin}, 2021 (remote). 

\ind ``Discovering microgenre communities in survey data on cultural practices.'' {\em University of Notre Dame Sociology Department Culture Workshop} (remote).

\ind ``What's wrong with social psychology?'' {\em Virtual Annual Meeting of the American Sociological Association}, 2021

\ind ``Inspired by: Pierre Bourdieu (1980, 1983, 1985).'' {\em Virtual Miniconference on the Social Logic of the Demand and Supply of Authenticity}, 2021.

\ind ``Concluding Remarks.'' {\em Cognition \& Migration workshop}, Paris, France, 2020 (remote).

\ind ``Incubators or diffusers? Examining the dynamic coupling of context and social ties across multiple foci.'' {\em University of Arizona School of Sociology Brown Bag Series},  2020 (remote).

\ind ``Linking social position and schematic disposition.'' {\em University of Michigan Sociology Department Colloquium}, Ann Arbor, MI, 2020.

\ind ``Conceptualizing culture in the social sciences: An analytic approach.''
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em Berkeley Haas Culture Conference}, Haas School of Business, University of California, Berkeley, Berkely, CA, 2020.
	\item[--] {\em Diverse Intelligences Summer Institute}, St. Andrews, Scotland, 2019.
\end{itemize}

\ind Panelist, \emph{Network Ecology Mini-Conference}. Stanford University, Palo Alto, CA, 2019.

\ind ``Cultural units beyond representation.'' {\em Diverse Intelligences Summer Institute}, St. Andrews, Scotland, 2019.

\ind ``Discovering taste communities in survey data.''

\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em University of Notre Dame, Department of Sociology Culture Workshop} (virtual), 2021.
	\item[--] {\em University of Arizona School of Sociology Brown Bag Series},  Tucson, AZ, 2019. 
    \item[--]{\em Jensen Lecture Series}, Department of Sociology, Duke University, Durham, North Carolina, 2018.
    \item[--]Keynote Address, {\em Understanding Everyday Participation Project Closing Conference}, Manchester, UK, 2018.
\end{itemize}

\ind ``Dual process models in social psychology and cultural sociology: Implications for the study of trust.'' Heidelberg Center for American Studies, Heidelberg University, Heidelberg, Germany, 2018. 

\ind ``Examining the link between different tie properties in ego networks.'' 
    \begin{itemize}[leftmargin=0.8in, topsep = 0pt]
    \setlength\itemsep{-0.55em}
    \item[--] Sociology Department Colloquium, Emory University, Atlanta, GA, 2019.
	\item[--] Department of Sociology and The Mitchell Centre for Social Network Analysis, University of Manchester, Manchester, UK, 2018.
\end{itemize}

\ind ``Social position and the complexity of schemas for cultural objects.'' {\em Brandeis University Sociology Department Colloquium}, Waltham, MA, 2018.



