
\ind ``Triadic evolution in a large-scale mobile phone network.'' 

\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] Hightower Seminar in Organization \& Management, Goizeta Business School, Emory University, Atlanta, GA, 2014.
	\item[--] MORS Colloquium, Haas Business School, University of California Berkeley, Berkeley, CA, 2014. 
\end{itemize}

\ind ``The end of theorists: The relevance, opportunities, and pitfalls of theorizing in sociology.'' \emph{Lewis Coser Memorial Lecture and Salon}, Annual Meeting of the American Sociological Association, San Francisco, CA, 2014.

\ind ``Bourdieu and the hard embodiment of culture: Methodological and theoretical challenges.'' \emph{Thematic Session on Bourdieu, Culture, and Empirical Research.} Annual Meeting of the American Sociological Association, San Francisco, CA, 2014.

\ind \emph{Symposium on Affinities of Language, Cultural Tool Kits, Institutional Logics: Advancing Strategies of Action}, Annual Meeting of the Academy of Management, Philadelphia, PA, 2014.

\ind \emph{Measuring Culture 2 Conference}, University of California at Santa Barbara, Santa Barbara, CA, 2014. 

\ind ``Beyond words: The conceptual basis of sociological theory.'' \emph{Gert H. Mueller Social Theory Speaker Series: The Craft of Doing Theory}, Department of Sociology, American University, Washington, D. C., 2014.

\ind ``Cultural omnivorousness and the perceived audience composition of musical styles." \emph{Culture and Inequality Workshop}, Department of Sociology, Princeton University, Princeton, NJ, 2014

\ind \emph{Special Session on What Should the Sociology of Culture and Cognition Look Like? --- A Conversation.}, Annual Meeting of the Eastern Sociological Society, Baltimore, MD, 2014.

\ind ``Persistence, churn, and decay in dynamic ego networks.'' Yale Institute for Network Science, Yale University, New Haven, CT, 2013.

\ind ``A theory of cultural embodiment.'' \emph{Center for Cultural Sociology Workshop}, Yale University, New Haven, CT, 2013.

\ind ``Age group dynamics and horizontal differentiation among Americans of different levels of education, 1993 - 2012.'' \emph{Emerging Cultural Capital and New Forms of Distinction Workshop}, London School of Economics, London, UK, 2013.

\ind ``The duality of persons and genres: Omnivorousness, cultural networks, and cultural holes.'' Keynote address at the \emph{The Social Spaces of Music: Networks, Worlds, Fields and Scenes Conference}, Centre for Research on Socio-Cultural Change, The University of Manchester, Manchester, UK, 2013.

\ind ``Cultural capital and the dynamics of personal networks.'' Department of Sociology, University of Illinois at Chicago, Chicago, IL, 2012.

\ind ``Measuring cultural holes.'' \emph{Measuring Culture 1 Conference}, University of British Columbia, Vancouver, BC, 2012.

\ind ``Cultural capital and the dynamics of personal networks.'' Department of Sociology, Columbia University, New York, NY, 2012.

\ind``Cultural tastes and the dynamics of personal networks.'' Department of Sociology, Duke University, Durham, NC, 2012.

\ind \emph{Quantifying Social Fields Conference}, held at the Institute for Research on Labor and Employment, University of California at Berkeley, Berkeley, California, 2012.

\ind ``Making distinctions: getting clear on some of the ‘hard problems’ in the study of culture.'' \emph{Social Theory and Evidence Workshop}, Department of Sociology, University of Chicago, Chicago, IL, 2012.

\ind ``Liking things, talking culture, and making friends.'' Department of Sociology, City College, City University of New York, New York, NY, 2012.

\ind ``How organizational theory can help network theorizing: Linking structure and dynamics via cross-level analogies.'' \emph{Scandinavian Consortium for Organizational Research (SCANCOR) Seminar}, Stanford University, Stanford, CA, 2012.
\ind  ``From culture to enculturation.''  \emph{SSIM Kickoff Meeting}, held at The Washington State Criminal Justice Training Commission, Burien, WA, 2011.

\ind  ``Embodied culture as procedure: Cognitive science and the link between subjective and objective culture.''  \emph{Symposium on Social Science and Sustainable Consumption}, Helsinki, Finland, 2011.

\ind  ``Taste and the logic of practice in \emph{Distinction}.'' \emph{Thirty Years after `Distinction' Conference},  Science Po, Paris, France, 2010.

\ind  ``Instituting organizations, cultural categories and structured inequality: The World Heritage Committee and the creation of outstanding universal value.'' \emph{Organizations \& Markets Workshop}, Booth School of Business, University of Chicago, Chicago, IL, 2010.

\ind  ``Instituting organizations, cultural categories and structured inequality: The World Heritage Committee and the creation of outstanding universal value.'' Pomona College, Claremont, California, 2010.
