\ind ``Institutional movement logics and the changing shape of the U.S. social movement field, 1960–1995,''
    \begin{itemize}[leftmargin=0.8in, topsep = 0pt]
    	\setlength\itemsep{-0.55em}
        \item[--] {\em Workshop on Social Organization}, Department of Sociology, Princeton University, Princeton, New Jersey, 2017.
        \item[--] {\em Culture and Politics Workshop}, Department of Sociology at the University of North Carolina Chapel Hill, Chapel Hill, North Carolina, 2017.
\end{itemize}

\ind Panelist, \emph{Conference on Networks and Culture}. Stanford University Graduate School of Business, Palo Alto, CA, 2017.

\ind ``Publishing theory at {\em ASR}.'' Invited panel on {\em How to Publish in Theory} Annual Meeting of the American Sociological Association, Montreal, Canada, 2017. 

\ind {\em Thematic Session on Boundaries and Fields}. Annual Meeting of the American Sociological Association, Montreal, Canada, 2017. 

\ind ``A procedural theory of culture.'' 
	\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
    	\item[--] Department of Sociology at the University of North Carolina Chapel Hill Colloquium Series, Chapel Hill, North Carolina, 2017.
    	\item[--] Department of Sociology at the University of Illinois at Chicago Colloquium Series, Chicago, Illinois, 2017.
    	\item[--] Department of Sociology at Princeton University Colloquium Series, Princeton, New Jersey, 2017.
      \item[--] New York University  Department of Sociology Culture Workshop, New York, New York, 2017.
    	\item[--] Keynote address at the {\em Cultural Sociology Lowlands Conference}. University of Amsterdam, Amsterdam, The Netherlands, 2017.
    \end{itemize} 

\ind ``Matching in cultural activities and persistence of social ties in the NetSense dataset.''
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
    \item[--] Sociology Department Colloquium, Dartmouth College, Hanover, New Hampshire, 2017.
	\item[--] Hanken Business School, Helsinki, Finland, 2017. 
    \item[--] Session on {\em Stability of Social Systems in the Age of Networked World} ARL NS CTA Annual Technical Meeting, Clayton Center, University of Delaware, Newark, Delaware, 2017.
    \item[--] Grenoble \'{E}cole de Management, Grenoble, France, 2017.
\end{itemize}

\ind \emph{Conference on Fields, Logics, Framing, and Cognition}. University of California at Berkeley, Berkeley, CA, 2017.

\ind ``The Mutual specification of genres and audiences: Reflective two-mode centralities in person-to-culture choice data.'' 
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em Formalizing Culture Workshop}, University of Bern, Bern, Switzerland, 2016. 
    \item[--] {\em `Culture Club' Seminar}, University of Amsterdam, Amsterdam, The Netherlands, 2017.
\end{itemize}

\ind ``Schematic logics and patterns of culture choice: Linking cognition and action in the sociology of taste.'' 
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em UC Berkeley Sociology Departmental Colloquium Series}, University of California, Berkeley, 2017.
	\item[--] {\em Social Research and Public Policy Seminar Series}, Department of Sociology, New York University, Abu Dhabi, 2016. 
	\item[--] {\em Sociology Colloquium}, Northwestern University, Evanston, IL, 2016.
    \item[--] {\em Department of Sociology Theory Workshop}, University of Iowa, Iowa City, IA, 2016.
\end{itemize}

\ind ``Publishing organization theory work at ASR.'' 
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] Hanken Business School, Helsinki, Finland, 2017. 
    \item[--] Grenoble \'{E}cole de Management, Grenoble, France, 2017.
	\item[--] {\em Social Interaction and Organizing at Northwestern (SION) Speaker Series}, Northwestern University, Evanston, IL, 2016. 
\end{itemize}

\ind ``Multilevel systems, interactive mechanisms, and the nature of culture.'' Section on Sociology of Culture Invited Session on {\em Recent Advances in the Sociology of Culture}. Annual Meetings of the American Sociological Association, Seattle, WA, 2016. 

\ind ``A Plea for Social Mechanisms in culture and cognition research: A multilevel systems approach.''  {\em New Directions in Culture and Cognition Mini-Conference}, Annual Meetings of the Eastern Sociological Society, Boston, MA, 2016.

\ind ``Linking position and perception: How social location shape the presumed characteristics of genre audiences.'' {\em University of British Columbia Sociology Department Seminar Series}, Vancouver, BC, 2016.

\ind ``Cultural objects as prisms: Perceived audience composition of musical styles as a resource for symbolic exclusion in the United States.'' 
\begin{itemize}[leftmargin=0.8in, topsep = 0pt]
	\setlength\itemsep{-0.55em}
	\item[--] {\em Grand Valley State University Sociology Department Colloquium}, Allendale, MI, 2017.
	\item[--] {\em Sociology Graduate Student Society (SGSS) Sponsored Talk}, University of Georgia, Athens, GA, 2016.
	\item[--] {\em Harvard University Sociology Department Colloquium Series}, Cambridge, MA, 2016.
	\item[--] {\em University of North Carolina at Charlotte Sociology Department Colloquium Series}, Charlotte, NC, 2015. 
	\item[--] {\em University of Arizona School of Sociology Brown Bag Series},  Tucson, AZ, 2015. 
\end{itemize} 

\ind ``(Prolegomenon to a) cultural dynamics: An analytic approach to processes of cultural change and reproduction.'' \emph{Micro-Macro Conference}, Stockholm, Sweden, 2015. 

\ind ``How sexual fields clarify the properties of fields in general,'' \emph{Thematic Session on Sexual Fields}, Annual Meeting of the American Sociological Association, Chicago, IL, 2015.

\ind ``The non-arbitrariness of cultural power: Grounding and motivation in cultural symbols." \emph{Thematic Session on The Sources of Cultural Power}, Annual Meeting of the American Sociological Association, Chicago, IL, 2015.

\emph{Measuring Culture Conference}. University of Notre Dame, Notre Dame Bend, IN, 2015. 
