
\ind ``Culture and categorization in an international organization: The case of UNESCO and the world heritage committee.'' \emph{Stanford University Graduate School of Business Organizational Behavior Seminar}, Stanford, CA, 2009.

\ind ``Seeing culture like UNESCO: Uncovering the building blocks of organizational cognition during unsettled times.'' \emph{University of Pennsylvania Sociology Department Colloquium Series}. Philadelphia, Pennsylvania, 2009.

\ind ``Cultural Capital in Interaction.'' \emph{MIT-Harvard Economic Sociology Seminar}. Cambridge, Massachusetts, 2009.

\ind ``Cultural Capital in Interaction.''  \emph{University of Notre Dame Sociology Department Brown Bag Seminar Series.} Notre Dame, Indiana, 2009.

\ind  ``Rethinking socialization theory from the point of view of practice theory.''  \emph{International workshop on the `Social Formations of Habit.'} Manchester University, United Kingdom, 2008.

\ind  ``Rethinking the relevance of Bourdieu's class theory for the sociology of taste.'' \emph{Northwestern University Sociology Department Culture and Society Workshop.} Evanston, Illinois, 2008.

\ind  ``Adaptation, reproduction and social change in the institutional analysis of organizations:  A dual cognition model.''  \emph{Junior Theorists Symposium}.  Harvard University, Boston, Massachusetts, 2008.

\ind  \textbf{Panelist}, special session on ``Culture and stratification,'' \emph{Culture Section Anniversary Symposium, Culture Section Miniconference}, Harvard University. Boston, Massachusetts, 2008.

\ind  ``The over-time stability of cultural taste:  Network versus cultural capital perspectives.''   \emph{Princeton University Sociology Department Culture Workshop}.  Princeton, New Jersey, 2008.

\ind  ``Cultural capital and social networks.''  \emph{University of Toronto Sociology Department Brown Bag Seminar Series.} Ontario, Canada, 2008.

\ind  \textbf{Participant}, \emph{Research on Orchestras Meeting}, Center for Arts and Cultural Policy Studies, Princeton University. Princeton, New Jersey, 2008.

\ind \textbf{Participant}, \emph{ John Templeton Foundation Human Personhood Conference}, University of Southern California, Los Angeles. California, 2008.

\ind  ``Rethinking the relevance of Bourdieu's class theory for the sociology of taste.'' \emph{University of Toronto Sociology Department Culture Workshop.} Ontario, Canada, 2008.

\ind  ``Cultural capital and social networks.''  \emph{University of Notre Dame Sociology Department Brown Bag Seminar Series.} Notre Dame, Indiana, 2008.

\ind  ``Can we still speak of cultural capital in the United States? An empirical analysis of the relationship between high-status cultural competence and wages.'' \emph{University of Chicago Workshop on Money, Markets and Consumption.} Chicago, Illinois, 2007.

\ind \textbf{Participant}, \emph{BYU Comparative Organizations Conference}, Sundance, Utah, 2007.

\ind  ``(Post 9/11) national pride as affective attachment to a large group:  A choice-process analysis.''  \emph{Indiana University Social Psychology, Health, and the Life Course (SHeL) Workshop.} Bloomington, Indiana, 2007.

\ind ``Dynamics of status and emotion in small groups: a formal model and simulation.'' \emph{University of Arizona Social Psychology Colloquium.}  Tucson, Arizona, 2005.

\ind ``The effect of economic and cultural globalization on anti-U.S. transnational terrorism 1971-2000.'' \emph{Stanford University Terrorism Research Group.} Stanford, CA, 2004.