
\ind {\bf Principal Investigator} (with Boles\l{}aw K. Szyma\'{n}ski [PI] and Hernan Makse [PI]), Human Networks and Data Science Program, Research Grant Award (\#2214216): ``Collaborative Research: HNDS-R: Dynamics and Mechanisms of Information Spread via Social Media.'' National Science Foundation, \$992,000 (2022-2025).

\ind\textbf{Project Advisory Board Member}. Mads Meier Jæger (PI), ``Mozart with Mom? Family Background, Cultural Participation, and Social Inequality.'' Velux Foundations funded project, University of Copenhagen, Denmark, \$DKK 5,400,000 (2018-2021).

\ind {\bf Principal Investigator} (Dissertation Improvement Grant for Brandon Sepulvado), Research Grant Award (SES-1702667): ``The Emergence of Disciplinary Networks: The Case of French Neurology.'' National Science Foundation, \$11,334.00 (2017-2018).

\ind {\bf Principal Investigator}, Network Science Collaborative Technology Alliance (NS-CTA), ``Influencing, Agitation Propagation, and Social Contagion in Empirical Networks and Data-Driven Models.'' United States Army Research Laboratory, \$180,000 (2016-2018).

\ind {\bf Principal Investigator}, Network Science Collaborative Technology Alliance (NS-CTA), ``Social Dynamics, Opinion Spreading, and Influencing in Social Networks.'' United States Army Research Laboratory, \$165,602 (2014-2016).

\ind {\bf Investigator} (with Nitesh Chawla [co-Investigator], David Hachen [co-Investigator], Tijana Milenkovi\'{c} [co-Investigator], Jessica Payne [co-Investigator], Aaron Striegel [co-Investigator], and Christian Poellabauer [co-Investigator]), ``NetHealth: Modeling the Co-evolution of Social Networks and Health Behaviors.'' National Institutes of Health (R01 HL117757-01A1), \$2,913,061 (2014-2018).
 
\ind {\bf Principal Investigator} (with  David Hachen [Lead-PI], Jeffrey Liew [PI], and Aaron Striegel [PI]), ``Using Smart Devices to Capture the Emotionality of Offline Communication.'' National Academies Keck Futures Initiative Grant, \$100,000 (2013-2014).

\ind {\bf Principal Investigator}, Network Science Collaborative Technology Alliance (NS-CTA), ``Social Dynamics, Opinion Spreading, and Influencing in Social Networks.'' United States Army Research Laboratory, \$84,714 (2013-2014).

\ind {\bf Principal Investigator} (Dissertation Improvement Grant for Sara Skiles), Research Grant Award (SES-1203426): ``Aesthetic Taste Expression and Symbolic Boundary Work.''  National Science Foundation, \$9,100 (2012-2013).

\ind {\bf Principal Investigator} (with Aaron Striegel [Lead-PI], David Hachen [PI], and Christian Poellabauer [PI] ), Division of Information \& Intelligent Systems, Social-Computational Systems Program, Research Grant Award (\#0968529): ``SoCS:  Explorations on the Effects of Pervasive Networking on Social Relationships and Resource Planning.'' National Science Foundation, \$802,325 (2010-2015).

\ind {\bf Co-Awardee} (with David Hachen) Grant to organize a ``Distinguished Speaker Series on Social Networks,'' Institute for Scholarship in the Liberal Arts (ISLA) Henkels Lecture Series, University of Notre Dame, \$15,000 (2009-2010).

\ind {\bf Principal Investigator} (with Zoltan Toroczkai [Lead-PI], Mark Alber PI], Nitesh Chawla [PI], and David Hachen [PI]), Division of Behavioral and Cognitive Sciences, Dynamics of Human Behavior Program, Research Grant Award (\#0826958): ``DHB: Longitudinal Analysis and Modeling of Large-Scale Social Networks Based on Cell Phone Records.''  National Science Foundation, \$711,770 (2008-2012).

