\ind {\bf Omar Lizardo}. 2009.  ``Social psychological processes as mechanisms for the explanation of cultural phenomena.'' Annual Meeting of the American Sociological Association. San Francisco, California.   

\ind David Hachen, {\bf Omar Lizardo}, Cheng Wang, Zoltan Toroczkai, Nitesh V. Chawla, Ryan Lichtenwalter, Troy Raeder, Anthony Strathman, and Zhechao Zhou.  2009. ``Reciprocity: The missing link.'' International School and Conference on Network Science (NetSci'09). Venice, Italy.

\ind David Hachen, {\bf Omar Lizardo}, Cheng Wang and Zhechao Zhou.  2009. ``Correlates of reciprocity in a large-scale communication network: A weighted edge approach.'' International Sunbelt Social Networks Conference (Sunbelt'09). San Diego, California. 

\ind {\bf Omar Lizardo}. 2008. ``Beyond the antinomies of structure: Recovering the insights of methodological structuralism.'' Annual Meeting of the American Sociological Association. Boston, Massachusetts.

\ind Albert J. Bergesen and {\bf Omar Lizardo}.  2008. ``Political economy of the world-system vs. world society/polity:  A crucial test of competing theoretical paradigms.'' Annual Meeting of the American Sociological Association. Boston, Massachusetts.   

\ind {\bf Omar Lizardo}. 2008. ``Cultural competence and network activation:  cultural capital as an enabling factor in the instrumental use of social ties.'' International Sunbelt Social Networks Conference (Sunbelt'08). St. Pete Beach, Florida.

\ind {\bf Omar Lizardo}. 2007.  ```Mirror neurons,' collective objects and the problem of transmission: Reconsidering Stephen Turner's critique of practice theory.'' Annual Meeting of the American Sociological Association. New York, New York.

\ind Jeff Larson and {\bf Omar Lizardo}. 2006. ``Collective memory and the identity politics of commodification: the case of Che Guevara.''  Annual Meeting of the American Sociological Association. Montreal, Canada.  

\ind {\bf Omar Lizardo}. 2006. ``Bourdieuian class position and interracial friendship choice.'' International Sunbelt Social Networks Conference (Sunbelt'06). Vancouver, British Columbia, Canada.  

