%\ind Mateusz Nurek, Joanna Ko\l{}aczek,  Rados\l{}aw Michalski, Boles\l{}aw K. Szyma\'{n}ski and {\bf Omar Lizardo}. ``CoDiNG: A Hybrid Opinion Model Based on Human Cognition.'' International School and Conference on Network Science 2025 (NetSci'25), Maastricht, The Netherlands. 

\ind {\bf Omar Lizardo}. ``The forward march of Categorical Tolerance in the United States.'' First Sociological Science Conference, Duke University, Durham, NC.

\ind Mateusz Nurek, Joanna Ko\l{}aczek,  Rados\l{}aw Michalski, Boles\l{}aw K. Szyma\'{n}ski and {\bf Omar Lizardo}. ``Modeling opinion formation using a new Cognitive Naming Game model.'' International Sunbelt Social Networks Conference (Sunbelt'24), Edinburgh, Scotland.	

\ind Michael Strand and {\bf Omar Lizardo}. ``Toward a Probabilistic Critique of the Sign.'' Annual Meeting of the American Sociological Association. Philadelphia, Pennsylvania. 

\ind Joel Stillerman and {\bf Omar Lizardo}. ``Barriers to Culture as Coordination: Reconsidering Erickson’s Thesis with Evidence from Chile’s Middle Classes.'' Annual Meeting of the American Sociological Association. Philadelphia, Pennsylvania. 

\ind Cheng Wang, {\bf Omar Lizardo} and David Hachen. ``Temporal patterns of the dyadic reciprocity among a sample of college students.'' International Sunbelt Social Networks Conference (Sunbelt'23), Portland, Oregon.	

\ind James Flamino, Ross DeVito, {\bf Omar Lizardo} and Boles\l{}aw K. Szyma\'{n}ski. ``Modeling the impact of cell phone interactions on memory imprints of members of social networks.'' 15$^{th}$ International Conference on Social Computing, Behavioral-Cultural Modeling \& Prediction and Behavior Representation in Modeling and Simulation (SBP-BRiMS'22), Pittsburgh, PA (Hybrid). 

\ind Cheng Wang, {\bf Omar Lizardo} and David Hachen. ``Temporal pattern of the friendship paradox among a sample of college students.''  International Sunbelt Social Networks Conference (Sunbelt'22), Cairns, Australia (remote).	

\ind Ethan Fridmanski, David Hachen, {\bf Omar Lizardo} and Cheng Wang. ``Do Lonely Birds Flock Together? Determinants of assortative mixing in college student networks.''	International Sunbelt Social Networks Conference (Sunbelt'22), Cairns, Australia (remote).

\ind David Hachen, {\bf Omar Lizardo} and Cheng Wang.	``Cross-Cutting Ethnoracial Social Ties Among Undergraduate Students at an Elite University.'' International Sunbelt Social Networks Conference (Sunbelt'22), Cairns, Australia (remote).

\ind Cheng Wang, Stephen Mattingly, Jessica Payne, {\bf Omar Lizardo} and David Hachen. ``Peer influence on personal sleep patterns.''	Networks 2021: A Joint Sunbelt and NetSci Conference: Combined meeting of the International Network for Social Network Analysis (Sunbelt'21), and the Network Science Society (NetSci'21) (virtual).

\ind David Hachen and {\bf Omar Lizardo}. ``The NetHealth project and data: New opportunities for studying social networks and health related behaviors.'' Networks 2021: A Joint Sunbelt and NetSci Conference: Combined meeting of the International Network for Social Network Analysis (Sunbelt'21), and the Network Science Society (NetSci'21) (virtual).

\ind David Hachen, {\bf Omar Lizardo}, Ethan Fridmanski and Cheng Wang.'' Do lonely birds flock together? Determinants of assortative mixing on loneliness among a cohort of first year college students.'' Networks 2021: A Joint Sunbelt and NetSci Conference: Combined meeting of the International Network for Social Network Analysis (Sunbelt'21), and the Network Science Society (NetSci'21) (virtual).

\ind Mateusz Nurek, Rados\l{}aw Michalski, {\bf Omar Lizardo} and Marian-Andrei Rizoiu. 2021. ``Predicting relationships and Big Five personality traits from telecommunication history based on Hawkes process.'' The 30th ACM International Conference on Information and Knowledge Management (virtual).

\ind Rados\l{}aw Michalski, Boles\l{}aw K. Szyma\'{n}ski, Przemys\l{}aw Kazienko, Christian Lebiere, {\bf Omar Lizardo} and Marcin Kulisiewicz. ``Cognition-driven temporal social networks." {\em Networks 2021: A Joint Conference of Sunbelt and NetSci} (virtual).

\ind Shikang Liu, David Hachen, {\bf Omar Lizardo}, Christian Poellabauer, Aaron Striegel and Tijana Milenkovic. 2020. ``The power of dynamic social networks to predict individuals' mental health.'' Pacific Symposium on Biocomputing (PSB '20), Big Island of Hawaii, HI. 
  

