
\ind Matthew Chandler and {\bf Omar Lizardo}. 2017. ``The shapes of solidarity: Theorizing emergent structures in social networks with abstract geometry.''  Annual Meeting of the American Sociological Association. Montreal, Canada. 

\ind Sudip Vhaduri, Christian Poellabauer, Aaron Striegel, {\bf Omar Lizardo} and David Hachen. 2017. ``Discovering places of Interest using sensor data from smartphones and wearables.'' 14th IEEE International Conference on Ubiquitous Intelligence and Computing (UIC'17). San Francisco, CA.

\ind Yuxiao Dong, {\bf Omar Lizardo} and Nitesh Chawla. 2017. ``Do the young live in a smaller world than the old? age-specific degrees of separation in human communication.'' 5th Conference on the Analysis of Mobile Phone Datasets (NetMob'17). Milan, Italy. 

\ind Ashwin Bahulkar, Boleslaw Szymanski, Kevin Chan and {\bf Omar Lizardo}. 2017.	``Coevolving networks in the NetSense dataset.'' International School and Conference on Network Science (NetSci'17). Indianapolis, Indiana. 

\ind {\bf Omar Lizardo}. 2017. ``Schematic logics and patterns of culture choice: Linking cognition and action in the sociology of taste.'' Culture and Cognition Mini-Conference, Annual Meetings of the Eastern Sociological Society, Philadelphia, PA.

\ind Jennifer Lena and {\bf Omar Lizardo}. 2016. ``The `omnivorous generation:' Artistic valorization and institutional work in the 20th century United States.'' Annual Meeting of the Social Science History Association. Chicago, Illinois. 

\ind Ashwin Bahulkar, Boleslaw Szymanski, Kevin Chan and {\bf Omar Lizardo}. 2016. ``Co-evolution of two networks representing different social relations in NetSense.'' 5th International Workshop on Complex Networks and their Applications (Complex Networks 2016). Milan, Italy. 

\ind Ashwin Bahulkar, Boleslaw Szymanski, {\bf Omar Lizardo}, Nitesh Chawla, Yuxiao Dong and Yang Yang.	2016. ``Analysis of link formation, persistence and dissolution in NetSense data.'' 6th Workshop on Social Network Analysis in Applications (SNAA'16).

\ind Rachael Purta, Stephen Mattingly, Lixing Song, {\bf Omar Lizardo}, David Hachen, Christian Poellabauer and Aaron Striegel. 2016. ``Experiences measuring sleep and physical activity patterns across a large college cohort with Fitbits.'' 20th International Symposium on Wearable Computers (ISWC'16). Heidelberg, Germany.

\ind Ashwin Bahulkar, Boleslaw Szymanski, {\bf Omar Lizardo}, Nitesh Chawla, Yuxiao Dong and Yang Yang.	2016. ``Analysis of link formation, persistence and dissolution in NetSense data.'' Proceedings of Advances in Social Network Analysis and Mining 2016 (P-ASONAM'16).

\ind David Hachen, {\bf Omar Lizardo}, Carlene Gundy and Cheng Wang. 2016. ``The dynamic coupling of two-mode social foci networks.'' Networks in the Global World Conference (NetGloW'16), St. Petersburg, Russia. 

\ind Yuxiao Dong, {\bf Omar Lizardo} and Nitesh Chawla. 2016. ``Longer degrees of separation between seniors in mobile communication.'' 2nd International Conference on Computational Social Science ($IC^2S^2$), Kellogg School of Management, Northwestern University, Evanston, Illinois. 

\ind David Hachen, {\bf Omar Lizardo}, Michael Penta, Matthew Chandler and Brandon Sepulvado. 2016. ``Ethnoracial status and tie decay in social networks: Linking triracial hierarchy and Simmelian tie theory.'' International Sunbelt Social Networks Conference (Sunbelt'16), Newport Beach, California.

\ind Brandon Sepulvado, David Hachen, {\bf Omar Lizardo} and Matthew Chandler. 2016. ``The big five personality traits in network formation.'' International Sunbelt Social Networks Conference (Sunbelt'16), Newport Beach, California.