\ind {\bf Omar Lizardo} and Jessica L. Collett. 2005. ``Why biology is not (religious) destiny: a second look at gender differences in religiosity.'' Annual Meeting of the American Sociological Association. Philadelphia, Pennsylvania.   

\ind {\bf Omar Lizardo}. 2005. ``Elastic social structures and compromised selves: some empirical implications of Goffman's embarrassment-interaction link.'' Annual Meeting of the American Sociological Association. Philadelphia, Pennsylvania.   

\ind {\bf Omar Lizardo}. 2005. ``Musical taste and culture consumption in Europe: a cross-national analysis.'' Annual meeting of the Pacific Sociological Association. Portland, Oregon. 

\ind {\bf Omar Lizardo}. 2005. ``What is structure?'' Annual meeting of the Pacific Sociological Association. Portland, Oregon.  

\ind  {\bf Omar Lizardo}. 2005. ``Latent association models for ego-network data.'' International Sunbelt Social Networks Conference (Sunbelt'05). Redondo Beach, California.

\ind {\bf Omar Lizardo}. 2004. ``The value of mass culture: highbrow and popular consumption and network outcomes.'' Annual Meeting of the American Sociological Association. San Francisco, California. 

\ind {\bf Omar Lizardo} and Jessica L. Collett. 2004. ``Socioeconomic status and the experience of anger.'' Annual Meeting of the American Sociological Association, San Francisco, California.  

\ind {\bf Omar Lizardo}. 2004. ``Towards an impure sociology: formalism, behavioral realism and the interdisciplinary challenge in social theory.'' Annual meeting of the Pacific Sociological Association. San Francisco, California.   

\ind {\bf Omar Lizardo}. 2003. ``The effect of employment status on gender differences in culture consumption.'' Annual meeting of the American Sociological Association. Atlanta, Georgia.  

\ind {\bf Omar Lizardo}. 2003. ``Towards a knowledge-interaction theory of group formation and inequality.'' Annual meeting of the Pacific Sociological Association. Pasadena, California.   

\ind {\bf Omar Lizardo}. 2003. ``Creating the reality of society: the role of cognitive mechanisms in Durkheim's theory of ritual.'' Annual meeting of the Pacific Sociological Association. Pasadena, California. 
 
\ind Albert J. Bergesen and {\bf Omar Lizardo}. 2002. ``Terrorism and the world-system.'' Annual Meeting of the American Sociological Association. Chicago, Illinois.

\ind Albert J. Bergesen and {\bf Omar Lizardo}. 2002. ``Terrorism and hegemonic decline.'' Political Economy of World-Systems Conference. University of California at Riverside. 