\noindent{\bf Steering Committee Member} 
\begin{itemize}[itemsep=-0.5ex]
    \item[--] 2019-present. \href{https://socopen.org/}{SocArXiv}.
\end{itemize}

\noindent{\bf PhD Teaching Board} 
\begin{itemize}[itemsep=-0.5ex]
    \item[--] 2017-present. Doctoral Program in {\em Analysis of Social and Economic Processes (ASEP)}, Maurizio Pisati (Director), Department of Sociology and Social Research, University of Milano-Bicocca, Italy. 
\end{itemize}

\noindent{\bf Advisory Board Member} 
\begin{itemize}[itemsep=-0.5ex]
    \item[--] 2023-2026. Department of Sociology, John Hopkins University.
    \item[--] 2023-2024. \textit{Duality@50} Conference, Monte Verit\`{a}, Ascona, Switzerland.
\end{itemize}

\noindent{\bf Program Committee Member} 
\begin{itemize}[itemsep=-0.5ex]
    \item[--] SI 2022, Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2022), Istanbul, Turkey.
    \item[--] 28th ACM/SIGKDD Conference on Knowledge Discovery and Data Mining (KDD 2022), Washington DC.
    \item[--] SI 2021, Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2021), (Virtual).
    \item[--] 7th International Conference on Computational Social Science (IC2S2-2021), Zurich, Switzerland.
    \item[--] 5th Edition of the Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2019), Vancouver, Canada. 
    \item[--] 4th Edition of the Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2018), Barcelona, Spain. 
    \item[--] 3rd Edition of the Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2017), Sidney, Australia. 
    \item[--] 3rd International Conference on Computational Social Science ($IC^2S^2$), Cologne, Germany, 2017. 
    \item[--] 2nd Edition of the Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2016), San Francisco, CA. 
    \item[--] 30 Years after ``Distinction'' Conference, at the Institut d'Etudes Politiques de Paris (Science Po), Paris, France, 2010.
    \item[--] American Sociological Association Section on Social Psychology, 2008.
\end{itemize}