\noindent{\bf American Sociological Association Committee Member}
\begin{itemize}[itemsep=-0.5ex] 
    \item[--] Section on Mathematical Sociology, Award for Progress in Mathematical Sociology Selection Committee, 2023.
    \item[--] Section on Consumers and Consumption Distinguished Scholarly Publication Award Selection Committee, 2023
    \item[--] W.E.B. Du Bois Career of Distinguished Scholarship Award Selection Committee, 2021-2023.
    \item[--] Section on the Sociology of Culture, Program Committee, 2022.
    \item[--] Section on the Sociology of Culture, Program Committee, 2021.
    \item[--] Lewis A. Coser Award for Theoretical Agenda-Setting Selection Committee, 2015.
    \item[--] Section on Comparative and Historical Sociology, Charles Tilly Best Article Award Selection Committee, 2015.
    \item[--] Committee on Nominations, 2014-2015. 
    \item[--] Section on Theory, Theory Prize Selection Committee, 2014.
    \item[--] Section on Theory, Theory Prize Selection Committee, 2012.
    \item[--] Section on Mathematical Sociology, Graduate Student Paper Award Selection Committee, 2012.
    \item[--] Section on the History of Sociology, Annual Publication Prize Award Selection Committee, 2010.
    \item[--] Section on the Sociology of Culture, Clifford Geertz Award for Best Article Selection Committee, 2009.
    \item[--] Section on Theory, Membership Committee, 2009.
    \item[--] Section on the Sociology of Culture, Committee on Nominations, 2007.
\end{itemize}

\noindent{\bf American Sociological Association Committee Chair}
\begin{itemize}[itemsep=-0.5ex]
    \item[--] W.E.B. Du Bois Career of Distinguished Scholarship Award Selection Committee, 2023.
    \item[--] Section on the Sociology of Culture, Clifford Geertz Award for Best Article Selection Committee, 2021.
    \item[--] Section on the Sociology of Culture, Committee on Nominations, 2019.
    \item[--] Shils-Coleman Graduate Student Paper Award, American Sociological Association Section on Theory, 2012.
\end{itemize}

\noindent{\bf American Sociological Association Elected Officer} 
\begin{itemize}[itemsep=-0.5ex]
    \item[--] Section on the Sociology of Culture (Chair), 2018-2019.
    \item[--] Section on the Sociology of Culture (Chair-Elect), 2017-2018.
    \item[--] Section on Theory (Council), 2011-2014.
    \item[--] Section on the Sociology of Culture (Council), 2011-2014.
\end{itemize}
\newpage