
\ind David Hachen, {\bf Omar Lizardo}, Michael Penta, Brandon Sepulvado and Matthew Chandler. 2015. ``Social tie formation, development and persistence: insights from the analysis of changes in the social networks of a college student cohort.'' International Conference on Computational Social Science ($IC^2S^2$), Helsinki, Finland.

\ind Jennifer Lena and {\bf Omar Lizardo}. 2015. ``Institutional entrepreneurship, artistic valorization, and the generation of cultural taste.''  Annual Meeting of the American Sociological Association. Chicago, Illinois. 

\ind {\bf Omar Lizardo} and Sara Skiles. 2014. ``Cultural Objects as prisms: Perceived audience composition of Musical Styles as a
Resource for Symbolic Exclusion in the United States.'' Annual Meeting of the Social Science History Association. Toronto, Ontario, Canada. 

\ind {\bf Omar Lizardo} and Melissa Fletcher Pirkey. 2014. `` Social cognitive mechanisms of category-based impression formation in markets.'' 17th Annual Organizational Ecology Conference, Barcelona, Spain.

\ind David Hachen and {\bf Omar Lizardo}. 2014. ``Dynamic ego networks.'' Temporal Networks, Human Dynamics, and Social Physics NetSci'14 Symposium (TnetSphys'14), Berkeley, California. 

\ind David Hachen and {\bf Omar Lizardo}. 2014. ``Growth, stability, change and inequality in dynamic ego networks.''  International Sunbelt Social Networks Conference (Sunbelt'14). St Pete's Beach, Florida. 

\ind Matthew Chandler and {\bf Omar Lizardo}. 2014. ``The shapes of solidarity: A formal network theory of community and society.'' International Sunbelt Social Networks Conference (Sunbelt'14). St Pete's Beach, Florida. 

\ind Jeff Larson and  {\bf Omar Lizardo}. 2014. ``An institutional logics approach to the analysis of social movement fields.'' Annual Meeting of the Eastern Sociological Society, Baltimore, Maryland.

\ind David Hachen and {\bf Omar Lizardo}. 2013. ``The effects of individual traits on the formation of social networks among first-year college students.''  International School and Conference on Network Science (NetSci'13), Copenhagen, Denmark.

\ind Aaron Striegel, Shu Liu, Lei Meng, Christian Poellabauer, David Hachen and {\bf Omar Lizardo}. 2013. ``Lessons Learned from the NetSense Smartphone Study.'' he 5th ACM HotPlanet Workshop (HotPlanet'13). Hong Kong. 

\ind David Hachen, {\bf Omar Lizardo}, Zoltan Toroczkai,  Cheng Wang, Anthony Strathman, Nitesh Chawla. 2012. ``Weighted reciprocity in human communication networks.''  Annual Meeting of the American Sociological Association. Denver, Colorado. 

\ind Cheng Wang, David Hachen and {\bf Omar Lizardo}. 2013. ``The Co-evolution of Communication Networks and Drinking Behaviors.'' AAAI Fall Symposium 2013 on
Social Networks and Social Contagion Web Analytics and Computational Social Science (SNSC'13). Arlington, Virginia.

\ind David Hachen, {\bf Omar Lizardo}, Michael Penta and Bryant Crubaugh.  2012. ``Netsense: a new network data collection platform for the study of the dynamics of social relationships.''  International Sunbelt Social Networks Conference (Sunbelt'12). St Pete's Beach, Florida. 

\ind Michael Penta, {\bf Omar Lizardo}, David Hachen and Bryant Crubaugh. 2012. ``The Ol' Ball and Chain: Negative effect of intimate long distance relationships on new tie formation.'' International Sunbelt Social Networks Conference (Sunbelt'12). St Pete's Beach, Florida.

\ind {\bf Omar Lizardo}.  2012. ``Beyond the antinomies of constructivism:  Practice theory, reference and the ontological stability of the social.''  14th Annual Philosophy of Social Science Roundtable.  University of Nebraska, Lincoln, Nebraska.

\ind {\bf Omar Lizardo} and Michael Strand. 2011.  ``Beyond `world images': Belief as embodied action in the world.''  Annual Meeting of the American Sociological Association. Las Vegas, Nevada. 

\ind {\bf Omar Lizardo} and David Hachen. 2011.  ``Dyadic reciprocity and the emergence of degree-assortativity in weighted social networks.''  International Sunbelt Social Networks Conference (Sunbelt'11). St Pete's Beach, Florida. 

\ind Robert M. Fishman and {\bf Omar Lizardo}. 2010.  ``Why Portugal and Spain came to diverge in cultural tastes: Legacies of polar opposite pathways to democracy.'' Annual Meeting of the Social Science History Association. Chicago, IL. 

\ind Robert M. Fishman and {\bf Omar Lizardo}. 2010.  ``How legacies of macro-political transformation shape patterns of cultural taste.'' Annual Meeting of the American Sociological Association. Atlanta, Georgia. 

\ind {\bf Omar Lizardo} and Melissa Fletcher Pirkey. 2010.  ``Instituting organizations, cultural categories and structured inequality.'' Annual Meeting of the American Sociological Association. Atlanta, Georgia. 

\ind {\bf Omar Lizardo}. 2010.  ``Rethinking \emph{habitus}: Cognitive dynamics and externalization.''  Paper presented for the Culture and Cognition Research Network.  Annual Meeting of the American Sociological Association. Atlanta, Georgia. 

\ind  {\bf Omar Lizardo} and David Hachen.  2010. `` Reciprocity and degree assortativity in human communication networks.'' International School and Conference on Network Science (NetSci'10). Cambridge, Massachusetts.



