\ind Ashwin Bahulkar, Boleslaw K. Szymanski, Kevin Chan and {\bf Omar Lizardo}. 2019. ``Modeling and predicting human social behavior.'' 25th ACM SIGKDD Conference on Knowledge Discovery and Data Mining, Anchorage, Alaska. 

\ind Louis Faust, Priscilla Jimenez-Pazmino, James K. Holland, {\bf Omar Lizardo}, David Hachen and Nitesh V. Chawla. 2019. ``What 30 Days tells us Aaout 3 Years: Leveraging early signs of user abandonment and compliance.'' 13th EAI International Conference on Pervasive Computing Technologies for Healthcare, Trento, Italy.

\ind Cheng Wang, {\bf Omar Lizardo} and David Hachen. 2018. ``Dynamics of local clustering in temporal social networks.'' 2nd North American Social Networks Conference, Washington, DC.

\ind Shikang Liu, David Hachen, {\bf Omar Lizardo}, Christian Poellabauer, Aaron Striegel and Tijana Milenkovic. 2018. ``Network analysis of the NetHealth data: Exploring co-evolution of individuals' social networks and physical activities.'' 2018 KDD Workshop on Machine Learning for Medicine and Healthcare, London, United Kingdom.

\ind David Hachen, {\bf Omar Lizardo} and Matthew Chandler. 2018. ``Examining the empirical linkages between different kinds of ties in dynamic ego networks.''  International Sunbelt Social Networks Conference (Sunbelt'18), Utrecht, The Netherlands.

\ind Ashwin Bahulkar, Boleslaw Szymanski, {\bf Omar Lizardo} and Kevin Chan. 2018. ``Impact of Attributes on Group Formation.'' 4th Edition of the Workshop on Social Influence, at the IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM 2018), Barcelona, Spain.

\ind Shikang Liu, David Hachen, {\bf Omar Lizardo}, Christian Poellabauer, Aaron Striegel and Tijana Milenkovic. 2018. ``Exploring co-evolution between individuals' social networks and physical activities in NetHealth data." Intelligent Systems for Molecular Biology Conference (ISMB'18), Chicago, Illinois. 

\ind Louis Faust, Priscilla Jimenez, David Hachen, {\bf Omar Lizardo}, Aaron Striegel and Nitesh V. Chawla. 2018. ``Long-term compliance habits: What early data tells us.''  Short Workshop on Next Steps Towards Long Term Self Tracking at the ACM CHI Conference on Human Factors in Computing Systems (CHI'18). Montreal, Canada.

\ind Radosław Michalski, Boleslaw Szymanski, Przemysław Kazienko, Christian Lebiere, {\bf Omar Lizardo} and Marcin Kulisiewicz. 2018. ``CogSNet: Cognition-driven social network.'' International School and Conference on Network Science (NetSci'18), Paris, France.

\ind Dustin Stoltz, Marshall Taylor and {\bf Omar Lizardo}. 2018. ``Functionaries: Institutional theory without institutions.'' Annual Meeting of the American Sociological Association. Philadelphia, Pennsylvania. 