\begin{itemize}[itemsep=-0.5ex] 
    \item[--] Selection Committee Chair, American Sociological Association W.E.B. Du Bois Career of Distinguished Scholarship Award, 2022.
    
    \item[--] Selection Committee, American Sociological Association W.E.B. Du Bois Career of Distinguished Scholarship Award, 2021-2023.
    
    \item[--] Committee on Nominations, American Sociological Association Section on the Sociology of Culture, 2019 (Chair).
    
    \item[--] Selection Committee, Lewis A. Coser Award for Theoretical Agenda-Setting, 2015.
    
    \item[--] Charles Tilly Best Article Award, American Sociological Association Section on Comparative Historical Sociology, 2015.
    
    \item[--] Theory Prize (Book), American Sociological Association Section on Theory, 2014.
    
    \item[--] Theory Prize (Book), American Sociological Association Section on Theory, 2012.
    
    \item[--] Shils-Coleman Graduate Student Paper Award, American Sociological Association Section on Theory (Chair), 2012.
    
    \item[--] Graduate Student Paper Award, American Sociological Association Section on Mathematical Sociology, 2012.
    
    \item[--] Annual Publication Prize Award, American Sociological Association Section on the History of Sociology, 2010.
    
    \item[--] Clifford Geertz Award for Best Article, American Sociological Association Section on the Sociology of Culture, 2009.
    
    \item[--] Membership Committee, American Sociological Association Section on Theory, 2009.
    
    \item[--] Committee on Nominations, American Sociological Association Section on the Sociology of Culture, 2007.
\end{itemize}