\noindent{\bf Conference Session Presider}

\begin{itemize}[itemsep=-0.5ex]
   \item[--] Regular session on ``The making and remaking of Science in bureaucratic and institutional context.'' Annual Meeting of the American Sociological Association, Los Angeles, California, 2022.
    
    \item[--] Thematic session on ``Intellectual displacements.'' Annual Meeting of the American Sociological Association, Los Angeles, California, 2022.
    
    \item[--] Regular session on ``Popular culture: Fields of cultural production.'' Annual Meeting of the American Sociological Association, New York, New York, 2019.
    
    \item[--] Regular session on ``Popular culture: Cultural taste and aesthetics.'' Annual Meeting of the American Sociological Association, New York, New York, 2019.
    
    \item[--] Session on  ``Can cultural sociology be an interscience?'' Annual Meeting of the American Sociological Association, Seattle, Washington, 2016.
    
    \item[--] Session on ``Habitus: Empirical explorations of how class-based dispositions shape daily life.'' Annual Meeting of the Eastern Sociological Society, Baltimore, MD, 2014.
    
    \item[--] Session on ``Realism and sociology.'' Annual Meeting of the American Sociological Association, Denver, Colorado, 2012.
    
    \item[--] Session on ``Music and genres: Boundaries, formation and identity.'' Annual Meeting of the Southern Sociological Society, New Orleans, Louisiana, 2012.
    
    \item[--] Session on ``Comparative views on changing social contracts.'' Annual Meeting of the Southern Sociological Society, New Orleans, Louisiana, 2012.
    
    \item[--] Session on ``New approaches to modeling cultural processes.'' Annual meeting of the American Sociological Association, Las Vegas, Nevada, 2011.
    
    \item[--] Session on ``Content and structure.'' Annual meeting of the American Sociological Association, San Francisco, California, 2009.
    
    \item[--] Session on ``The global Umma: The imagined community of radical Islam.''  Annual meeting of the American Sociological Association, San Francisco, California, 2009.
    
    \item[--] Section on the Sociology of Culture and Section on Social Psychology joint invited session on ``What can social psychologists learn from cultural sociology?''   Annual meeting of the American Sociological Association, Atlanta, Georgia, 2010.
\end{itemize}