\begin{itemize}[itemsep=-0.5ex]
    \item[--] Regular session on ``The making and remaking of Science in bureaucratic and institutional context.'' Annual Meeting of the American Sociological Association, Los Angeles, California, 2022.
    
    \item[--] Thematic session on ``Intellectual displacements.'' Annual Meeting of the American Sociological Association, Los Angeles, California, 2022.
    
    \item[--] Regular session on ``Popular culture: Fields of cultural production .'' Annual Meeting of the American Sociological Association, New York, New York, 2019.
    
    \item[--] Regular session on ``Popular culture: Cultural taste and aesthetics.'' Annual Meeting of the American Sociological Association, New York, New York, 2019.
    
    \item[--] Session on ``Race, emotion and social networks.'' Annual Meeting of the American Sociological Association, Philadelphia, Pennsylvania, 2018.
    
    \item[--] Session on  ``Can cultural sociology be an interscience?'' Annual Meeting of the American Sociological Association, Seattle, Washington, 2016.
    
    \item[--] Regular session on ``Habitus''   Annual meeting of the American Sociological Association, San Francisco, California, 2014.
    
    \item[--] Special session on ``Cognitive science and methodological practice in sociology: Implications, challenges and prospects.''  Annual meeting of the American Sociological Association, Las Vegas, Nevada, 2011.
    
    \item[--] Session on ``Exploring the role of culture in the creation and reproduction of social boundaries''   Annual meeting of the Pacific Sociological Association, Seattle, Washington, 2011.
    
    \item[--] Joint invited session (Section on the Sociology of Culture and Section on Social Psychology) on ``What can social psychologists learn from cultural sociology?''   Annual meeting of the American Sociological Association, Atlanta, Georgia, 2010.
    
    \item[--] Session on ``What's new at the intersection of culture and cognition?'' Annual meeting of the American Sociological Association, San Francisco, California, 2009.
    
    \item[--] Roundtables for the Section on the Sociology of Culture, Annual meeting of the American Sociological Association, New York, New York, 2007.
    
    \item[--] Session on ``Comparative approaches to cultural taste and culture consumption.'' Annual meeting of the Pacific Sociological Association, Portland, Oregon, 2005.
    
    \item[--] (with Michelle Bata) Session on ``Local responses to globalization.'' Annual meeting of the Pacific Sociological Association, San Francisco, California, 2004.
\end{itemize}